Betting and Belief: Prediction Markets and Attribution of Climate Change

### 2016-04-19 presentation/present.Rmd
presentation with diagrams for model dynamics explanation

- Scientific consensus on anthropogenic nature of climate change strongly increased.
- BUT, beliefs about climate change did not evolve much within public. Increasingly politicized.
- Prediction markets: participants can "put their money where their mouths are."
- High prediction accuracy and information aggregation.
- Do they also change beliefs?

@@

- Research question: *whether, and under what social and climate conditions, might prediction markets be useful for increasing convergence of climate beliefs?*
- Prediction markets (hypermind.com, betfair.com, and predictit.org) focus on near term events such as elections months away, so difficult to extrapolate to climate case.
- Investigating unobservable beliefs of traders. 
- So, simulation modeling informed by climate and economic theory.

@@

@@

1. Trader agents estimate forecasting model with data.
2. Make predictions for climate for 6 yrs from now to assign expected value to temp securities.
3. Trade on market.
4. Payoffs for owners of security that was correct.
5. Decide whether to adopt neighbors model based on cumulative earnings.

>>>>

- Scientific consensus on anthropogenic climate change increased.
- BUT, beliefs about climate change did not evolve much within public.
- Prediction markets: participants can "put their money where their mouths are."
- High prediction accuracy, efficient information aggregation.
- Do they also change beliefs?

@@

- *Whether, and under what social and climate conditions, might prediction markets be useful for increasing convergence of climate beliefs?*
- Prediction markets focus on near term events such as elections months away, so difficult to extrapolate to climate case.
- Investigating unobservable beliefs of traders. 
- So, simulation modeling informed by climate and economic theory.

@@

## Trader Beliefs

- At initialization approximately half of traders use true data-generating model to make predictions. 
- Traders using true model not necessarily perfectly accurate. 
- Although correct *functional form* of model, still need to calibrate on limited noisy data.

@@

1. Trader agents estimate forecasting model.
2. Make predictions for climate for 6 yrs from now to assign expected value to temp securities.
3. Trade.
4. Payoffs for owners of security that was correct.
5. Decide whether to adopt neighbors model based on cumulative earnings.
